2-D Photosynthesis Model

### 2023-09-25 ms/ms.Rmd
updated bibliography

  It consists of two paragraphs.
keywords:
  - stomatal patterning
  - Aribidopsis thaliana
  - amphistomatous leaves
  - photosynthesis modeling
  - optimizing photosynthesis
  - CO$_2$ diffusion
fontsize: 12pt
#spacing: halfline # could also be oneline
#classoptions:
#  - endnotes
bibliography: 8_17.bib
#csl: mycitationstyle.csl
link-citations: yes
output: rticles::oup_article
#urlcolor: orange
#linkcolor: green
#citecolor: red
header-includes:
 - \usepackage[nomarkers,tablesfirst]{endfloat} # For figures and tables at end
 - \usepackage{lineno} # For line numbering
 - \linenumbers # For line numbering
---

>>>>

  It consists of two paragraphs.
keywords:
  - stomatal patterning
  - Aribidopsis thaliana
  - amphistomatous leaves
  - photosynthesis modeling
  - optimizing photosynthesis
  - CO$_2$ diffusion
fontsize: 12pt
#spacing: halfline # could also be oneline
#classoptions:
#  - endnotes
bibliography: stomata-spacing.bib
#csl: mycitationstyle.csl
link-citations: yes
output: rticles::oup_article
#urlcolor: orange
#linkcolor: green
#citecolor: red
header-includes:
 - \usepackage[nomarkers,tablesfirst]{endfloat} # For figures and tables at end
 - \usepackage{lineno} # For line numbering
 - \linenumbers # For line numbering
---

### 2023-09-25 ms/si.qmd
updated bibliography

---
title: "2-D Photosynthesis Model"
format: docx
editor: visual
bibliography: ../references.bib
---

@@

@@

library(dplyr)
library(ggforce)
library(ggplot2)
library(tidyr)

@@

>>>>

---
title: "2-D Photosynthesis Model"
format: docx
editor: visual
bibliography: ../ms/stomata-spacing.bib
---

@@

## Code

I've copied the *R* code to set up the model and solve it if you want to copy and paste on your own machine. First, here are the packages you'll need.

```{r, packages, message=FALSE}

library(dplyr)
library(ggforce)
library(ggplot2)
library(readr)
library(tidyr)

```{r, functions, echo=FALSE, message=FALSE}

source("../r/functions.R")

@@

@@

```{r, glossary, echo = FALSE, message = FALSE}

readr::read_csv("../raw-data/2d-pm-parameters.csv") |>
  filter(!calculated) |>
  mutate(Value = glue::glue("${x}$", x = scientize(default_value))) |>
  select(Name = name, Symbol = symbol, Value, Units = units, Notes = notes) |>
  knitr::kable()
```

## References
